\section{Graphs}
\todo{Flows, matching, euler tour, bridges+art. points, CC, mst Prim}

\subsection{Conventions}
\begin{lstlisting}
constexpr ll INF = 1e18;
\end{lstlisting}
V := number of vertices, E := number of edges

\subsection{Dijkstra - Single Source Shortest Path}
\bigo{ElogV} , fails with negative weight cycles.

\verb|vector<ll> dist = dijkstra(adj_list, src);| \\
\verb|dist[u]| := distance between node \verb|src| and \verb|u| \\
\verb|dist[u]| = \verb|INF| if there's no path between \verb|src| and \verb|u|
\lstinputlisting{source/dijkstra.cpp}


\subsection{Bellman-Ford - Single Source Shortest Path}
\bigo{VE}, handles negative weight edges and cycles.

Edges are represented by an \verb|array<int, 3> edge| s.t.: \\
\verb|edge[0] = from, edge[1] = to, edge[2] = cost| \\
\verb|vector<ll> dist = bellman_ford(edge_list, v, src);|, v = number of vertices \\
\verb|dist[u]| := distance between node \verb|src| and \verb|v| \\
\verb|dist[u]| = \verb|INF| if there's no path between \verb|src| and \verb|v| \\
\verb|dist[u]| = \verb|-INF| if there's a negative-weight cycle between \verb|src| and \verb|v|
\lstinputlisting{source/bellman_ford.cpp}


\subsection{Floyd Warshall - All-pairs Shortest Path}
\bigo{V^3}

Takes an adjacency matrix as input, with \verb|g[u][v]|=INF if there's no edge between \verb|u| and \verb|v|. Handles negative cycles. \\
\verb|auto dist = floyd_warshall(adjacency_matrix);| \\
\verb|dist[u][v]| := distance between node \verb|u| and \verb|v| \\
\verb|dist[u][v]| = \verb|INF| if there's no path between \verb|u| and \verb|v| \\
\verb|dist[u][v]| = \verb|-INF| if the path between \verb|u| and \verb|v| can be made arbitrarily short by going through a negative weight cycle
\lstinputlisting{source/floyd_warshall.cpp}

\subsection{0/1 BFS - SSSP with binary weights}
\bigo{V+E}, handles graphs where all edges have a weight of $0$ or $1$.
\verb|vector<ll> dist = bfs01(adj_list, src);| \\
\verb|dist[u]| := distance between node \verb|src| and \verb|u| \\
\verb|dist[u]| = \verb|INF| if there's no path between \verb|src| and \verb|u|
\lstinputlisting{source/bfs01.cpp}

\subsection{Khan - Topological Sort}
\bigo{V + E}

\verb|vi order = topological_sort(adjacency_list);| \\
if the graph is not a DAG, order will be empty
\lstinputlisting{source/topological_sort.cpp}


\subsection{Prim's Algorithm (Dense Graphs) - Minimum Spanning Tree}
\bigo{V^2}

Takes an adjacency matrix as input, with \verb|g[u][v]|=INF if there's no edge between \verb|u| and \verb|v|. \\
Returns the adjacency list of the undirected weighted minimum spanning tree of the given graph. \\
If the graph is not connected it returns an empty list. \\
\verb|auto mst = prim(adjacency_matrix);| \\
\lstinputlisting{source/prim_mst_dense.cpp}


\subsection{Prim's Algorithm (Sparse Graphs) - Minimum Spanning Tree}
\bigo{Elog(V)}

Takes an adjacency list as input \\
Returns the adjacency list of the undirected weighted minimum spanning tree of the given graph. \\
If the graph is not connected it returns an empty list. \\
\verb|auto mst = prim(adjacency_list);| \\
\lstinputlisting{source/prim_mst_sparse.cpp}


\todo{Add compressed graph}
\subsection{Kosaraju - Strongly Connected Components}
\bigo{V + E}

\verb|Kosaraju kosaraju{adjacency_list};| \\
\verb|kosaraju.cc| will store the total number of strongly connected components \\
\verb|kosaraju.comp[u]| will store an integer in range [0, cc) representing the strongly connected component of u
\lstinputlisting{source/kosaraju.cpp}
